---
title: "Mini_project"
author: "Sandeep Vemulapalli and Pavan Yachamaneni"
date: "2022-10-27"
output: html_document
---

```{r , echo=FALSE}
set.seed(29071000)
sim <- 10000
nodes <- 15
maxedge <- replicate(sim,0)
maxloc <- replicate(sim,0)
fullstore <- matrix(,ncol=15)
affnity_mat=matrix(0,nrow=nodes,ncol = nodes)
for(i in 1:sim){
  dummy = matrix(0,nrow=nodes,ncol = nodes)
  edges <- replicate(nodes, 0)
  edges[1] = 1
  edges[2] = 1
  dummy[1,2]=1
  dummy[2,1]=1
  for(j in 3:nodes){
    sumedge <- sum(edges)
    edges[j] = 1
    new <- sample(1:(j-1),1, prob = edges[1:(j-1)]/sumedge)
    edges[new[1]]=edges[new]+1
    dummy[j,new]=1
    dummy[new,j]=1
  }
  fullstore <- rbind(fullstore,edges)
  affnity_mat=affnity_mat+dummy
}

fullstore<- fullstore[2:10001,]
row.names(fullstore)<-c(1:10000)
fullstore=t(fullstore)
fullstore[,1:20]
```


### Observation
- In the Distance matrix, initial nodes has higher chances of getting connections and subsequently making its probability higher for upcoming child nodes and it repeats contineously.


### Creating Affinity Matrix
- Affinity or similarity matrix tells how close the 2 points in a space. Usually in graph scenario, neighbours are connected with minimum distance, so finding affinity matrix explicitely tells wether the given 2 points in the graph are neighbours or not.

$$ Affinity \;Matrix \;=\exp(-\beta * Distance\;Matrix^2)\;\;;where \;\;\beta=\frac{1}{2\sigma^2} $$

```{r , echo=FALSE}
library(fields)
library(reshape2)
library(SNFtool)
library(ggcorrplot)
library(tidyverse)
distance_matrix = (dist2(as.matrix(fullstore),as.matrix(fullstore)))^(1/2)
standard_deviation <- sd(distance_matrix)
real_affinity_mat <- exp(-distance_matrix^2/ (2*standard_deviation^2))
real_affinity_mat
```


```{r , echo=FALSE}
affnity_mat

```

### Result shows the affinity matrix 15 preferential attachment model nodes when performed with 10000 simulations.
### In each field of the matrix represents in what number of simulation, the 2 nodes are connected.



## Edge Statistics:
- We can plot the histogram of each node and see what distribution does node follows after completing 10000 simulations.
```{r,echo=FALSE}

fullstoredf = as.data.frame(t(fullstore))
ggplot(fullstoredf, aes(x=V1)) + geom_histogram(binwidth = 0.5,color="white", fill="green") + scale_x_continuous(name = "Edge distribution for Node 1") + scale_y_continuous(name = "Count")
ggplot(fullstoredf, aes(x=V3)) + geom_histogram(binwidth = 0.5,color="white", fill="blue") + scale_x_continuous(name = "Edge distribution for Node 3") + scale_y_continuous(name = "Count")
ggplot(fullstoredf, aes(x=V7)) + geom_histogram(binwidth = 0.5,color="white", fill="pink") + scale_x_continuous(name = "Edge distribution for Node 7") + scale_y_continuous(name = "Count")
ggplot(fullstoredf, aes(x=V9)) + geom_histogram(binwidth = 0.5,color="white", fill="orange") + scale_x_continuous(name = "Edge distribution for Node 9") + scale_y_continuous(name = "Count")
ggplot(fullstoredf, aes(x=V11)) + geom_histogram(binwidth = 0.5,color="white", fill="yellow") + scale_x_continuous(name = "Edge distribution for Node 11") + scale_y_continuous(name = "Count")


```

### Observation: Upon moving forward to higher nodes skewness is increasing as it is observed that later nodes are mostly connected to initial nodes which makes the probability higher.

## Doing for 100 nodes
```{r,echo=FALSE}
set.seed(290710)
sim <- 1000
nodes <- 100
maxedge <- replicate(sim,0)
maxloc <- replicate(sim,0)
fullstore100 <- matrix(,ncol=100)
for(i in 1:sim){
  edges <- replicate(nodes, 0)
  edges[1] = 1
  edges[2] = 1
  for(j in 3:nodes){
    sumedge <- sum(edges)
    edges[j] = 1
    new <- sample(1:(j-1),1, prob = edges[1:(j-1)]/sumedge)
    edges[new[1]]=edges[new]+1
  }
  fullstore100 <- rbind(fullstore100,edges)
}

fullstore100<- fullstore100[2:1001,]
row.names(fullstore100)<-c(1:1000)
fullstore100=t(fullstore100)
fullstore100[1:20,1:20]

```
```{r,echo=FALSE}
fullstore100df = as.data.frame(t(fullstore100))
ggplot(fullstore100df, aes(x=V10)) + geom_histogram(binwidth = 0.5,color="white", fill="royalblue4") + scale_x_continuous(name = "Edge distribution for Node 10") +
scale_y_continuous(name = "Count")
ggplot(fullstore100df, aes(x=V25)) + geom_histogram(binwidth = 0.5,color="white", fill="blue") + scale_x_continuous(name = "Edge distribution for Node 25") +
scale_y_continuous(name = "Count")
ggplot(fullstore100df, aes(x=V50)) + geom_histogram(binwidth = 0.5,color="white", fill="royalblue") + scale_x_continuous(name = "Edge distribution for Node 50") +
scale_y_continuous(name = "Count")
ggplot(fullstore100df, aes(x=V75)) + geom_histogram(binwidth = 0.5,color="white", fill="royalblue") + scale_x_continuous(name = "Edge distribution for Node 75") +
scale_y_continuous(name = "Count")
ggplot(fullstore100df, aes(x=V99)) + geom_histogram(binwidth = 0.5,color="white", fill="royalblue") + scale_x_continuous(name = "Edge distribution for Node 100") +
scale_y_continuous(name = "Count")
```

### Observation for 100 nodes is similar to that off 15 nodes but their rates is further skewing down rapidly that with 15 nodes making larger number nodes biased towards samller connections that has large descrepensies to samller numbered nodes.x



